---
title: "Assignment 2"
author: "Insert My Name"
date: "2024-09-25"
output: html_document # you can change to other output format if you want
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
   #library(tidyverse)
   #install.packages("Stat2Data")
   #library(Stat2Data)
   data("Hawks")
   head(Hawks)
```

# 1. Data Wrangling

## 1.1 (Q1)   
```{r}
hSF <- Hawks %>%
        filter(Species == "RT" & Weight >= 1000) %>%
        select("Wing", "Weight", "Tail")
hSF
```

## 1.1 (Q2) 
# There are three variables in this data frame(Wing, Weight, Tail). 
# For the ML practitioner, I will tell them each sample in the dataset have three features vetor, they are Wing, Weight and Tail.
```{r}
ncol(hSF)  # 3
nrow(hSF)  # 398
```
# The Number of examples is same as the number of row, and examples, observations, case is the same meaning, both of them are same.

## 1.2 (Q1)
```{r}
head(hSF %>% arrange(Wing))
```

## 1.3 (Q1)
```{r}
species_code <- c("CH", "RT", "SS")
species_name_full <- c("Cooper's", "Red-tailed", "Sharp-shinned")
hawkSpeciesNameCodes <- data.frame(species_code, species_name_full)
hawkSpeciesNameCodes
```

## 1.3 (Q2)
```{r}
hawksFullName <- Hawks %>%
                 left_join(hawkSpeciesNameCodes, by = c("Species" = "species_code")) %>%
                 select(-Species) %>%
                 rename(Species = species_name_full)

hawksFullName
```

## 1.3 (Q3)
```{r}
hawksFullName %>%
  select(Species, Wing, Weight) %>%
  head(7)
```

# It's important to choose left join because we need to keep Hawks's data, and we can ingore the data that the hawkSpeciesNameCodes' s can't matching with. If not matching, It could fill with null.
# inner_join can lead to if there's one coloum doesn't matching, this coloum will be abandon. right_join will keep the right side data and to give up the left side data. The full_join will keep both side of the data, and one side of this coloum will be NA.


## 1.4 (Q1)
```{r}
hawksWithBMI <- Hawks %>%
                mutate(bird_BMI = 1000 * Weight / (Wing ^ 2)) %>%
                select(Species, bird_BMI) %>%
                arrange(desc(bird_BMI))
hawksWithBMI
```


## 1.5 (Q1)
```{r}
hawksSummarize <- hawksFullName %>%
                  group_by(Species) %>%
                  summarize(
                    num_rows = n(),
                    mn_wing = mean(Wing / 10, na.rm = TRUE),
                    nd_wing = median(Wing / 10, na.rm = TRUE),
                    t_mn_wing = mean(Wing / 10, trim = 0.1, na.rm = TRUE),
                    b_wt_ratio = max(Wing / Tail, na.rm = TRUE)
                  )
hawksSummarize
```

# 1.5 (Q2)
```{r}
missingSummary <- hawksFullName %>%
                  select(Species, Wing, Weight, Culmen, Hallux, Tail, StandardTail, Tarsus, Crop) %>%
                  group_by(Species) %>%
                  summarize(across(everything(), ~sum(is.na(.))))
missingSummary
```


