---
title: "Assignment_03"
author: "noah"
date: "2024-10-01"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(Stat2Data)
data("Hawks")
```

# 1.Visualisation
# Question 1
```{r}
hawksSmall <- drop_na(select(Hawks,Age,Day,Month,Year,CaptureTime,Species,Wing,Weight,Tail))
dim(hawksSmall)
head(hawksSmall)

```


# Question 2
```{r}
ggplot(data = hawksSmall, aes(x = Weight)) +
         geom_histogram(binwidth = 10) +
         xlab("Weight") +
         ylab("Count")

```


# Question 3
```{r}
ggplot(data = hawksSmall, aes(x = Tail)) +
         geom_density(adjust=0.5) +
         xlab("Tail length") +
         ylab("Count")

ggplot(data = hawksSmall, aes(x = Tail)) +
         geom_density(adjust=2) +
         xlab("Tail length") +
         ylab("Count")
```

# There are three peak value in the first plot, which mean it was Trimodal. And the second plot shows that two peak, it's Bimodal.
# adjust = 0.5: The curve more narrower and more sharper. And adjust = 2: The curve are more smoother.

# Question 4
```{r}
ggplot(data = hawksSmall, aes(x = Tail, color = Species)) +
         geom_density(adjust = 2) +
         xlab("Tail length") +
         ylab("Count")
```

# Question 5
```{r}
ggplot(data = hawksSmall, aes(x = Tail, y = Species, fill = Species)) +
  geom_violin() +
  geom_boxplot(width = 0.1, outlier.colour = "red") +
  xlab("Tail length") +
  ylab("Species")

```

# Question 6
```{r}
ggplot(data = hawksSmall, aes(x = Tail, y = Weight)) +
  geom_point(aes(color = Species, shape = Species)) +
  xlab("Tail(mm)")+
  ylab("Weight(mm)")

```

# Each color represent different species, same as the shape of the points. Red circle represent CH, Green triangles represent RT, and Blue square represent SS. The X-axis represent Tail length, and Y-axis represent Weight.


# Question 7

# As the length of the tail increases, so does the weight. the RT has a greater range of weights.
```{r}
ggplot(data = hawksSmall, aes(x = Tail, y = Weight)) +
  geom_point(aes(color = Species)) +
  geom_smooth(method = "lm") +
  facet_wrap(~Species, scales = "free_y") +
  xlab("Tail(mm)") +
  ylab("Weight(mm)")

```


# Question 8
```{r}
# max(hawksSmall %>% select("Weight"))
heaviest_hawks <- hawksSmall %>%
  filter(Weight == max(Weight, na.rm = TRUE)) %>%
  select(Weight, Tail)
heaviest_hawks

ggplot(data = hawksSmall, aes(x = Tail, y = Weight)) +
  geom_point(aes(color = Species, shape = Species)) +
  geom_curve(x = 190, xend = 195, y = 1600, yend = 2020, arrow = arrow(length = unit(0.5, 'cm')), curvature = 0.1) +
  geom_text(x = 190, y = 1550, label = "heavest hawk") +
  xlab("Tail(mm)")+
  ylab("Weight(mm)")

```



# Finite probability spaces
# Question 1
$$
P(Z = z) = \binom{22}{z} \cdot \left( \frac{3}{10} \right)^z \cdot \left( \frac{7}{10} \right)^{22 - z}
$$

# Question 2
```{r}
prob_red_spheres <- function(z) {
  return(choose(22, z) * (3/10)^z * (7/10)^(22-z))
}

prob_red_spheres(10)

```

# Question 3
```{r}
prob_by_num_reds <- data.frame(
  num_reds = 0:22,
  prob = sapply(0:22, prob_red_spheres)
)

head(prob_by_num_reds, 3)

```

# Question 4
```{r}
ggplot(data = prob_by_num_reds, aes(x = num_reds, y = prob)) +
  geom_line() +
  labs(x = "Num of reds", y = "Probability")

```

# Question 5
```{r}
sample(10, 22, replace = TRUE)
set.seed(111)
sample(10, 22, replace = TRUE)

```

# Question 6
```{r}
# 模拟 1000 次抽样
num_trials <- 1000
set.seed(0)
sampling_sim <- data.frame(trial = 1:num_trials) %>%
  mutate(sample_balls = replicate(num_trials, sample(10, 22, replace = TRUE)))

# 计算每次抽样中红色球的数量
sampling_sim <- sampling_sim %>%
  mutate(num_reds = sapply(sample_balls, function(x) sum(x <= 3)))

# 统计每个红色球数量的频率
num_reds_in_sim <- sampling_sim$num_reds
prob_by_num_reds <- prob_by_num_reds %>%
  mutate(predicted_prob = sapply(0:22, function(z) sum(num_reds_in_sim == z) / num_trials))


```

# Question 7
```{r}
ggplot(prob_by_num_reds) +
  geom_line(aes(x = num_reds, y = prob, color = "Theoretical")) +
  geom_line(aes(x = num_reds, y = predicted_prob, color = "Simulated"), linetype = "dashed") +
  xlab("Number of reds") +
  ylab("Probability") +
  theme_minimal()

```












